### 2023-03-22 src/paper.tex
Inventory grammar fix

\Ex
\begin{equation*}
  \begin{aligned}
    Doc &\Arrow inventory(\Kleene{Item})\\
    Item &\Arrow desk(Desk) \Union chair(Chair) \Union computer(Computer) \\
    Info &\Arrow Location \Seq \KleenePlus{User}\\
    Location &\Arrow location(Building \Seq Room)\\
    User &\Arrow user(Name \Seq Surname \Seq \Opt{Role})\\
    Desk &\Arrow Info \Seq standing(Standing)\\
    Chair &\Arrow Info\\
    Computer &\Arrow Info \Seq Cpu \Seq Ram \Seq Disk\\
    Name &\Arrow text()\\
    Surname &\Arrow text()\\
    Role &\Arrow text()\\
    Building &\Arrow text()\\
    Room &\Arrow int()\\
    Standing &\Arrow bool()\\
    Cpu &\Arrow float()\\
    Ram &\Arrow float()\\
    Disk &\Arrow float()\\
  \end{aligned}
\end{equation*}

>>>>

\Ex
\begin{equation*}
  \begin{aligned}
    Doc &\Arrow inventory(\Kleene{Item})\\
    Item &\Arrow desk(Desk) \Union chair(Chair) \Union computer(Computer) \\
    Info &\Arrow location(Location) \Seq \KleenePlus{user(User)}\\
    Location &\Arrow building(string()) \Seq room(Room)\\
    User &\Arrow name(Capitalized) \Seq surname(Capitalized) \Seq \Opt{role(Role)}\\
    Desk &\Arrow Info \Seq standing(boolean())\\
    Chair &\Arrow Info\\
    Computer &\Arrow Info \Seq cpu(Quantity) \Seq memory(Quantity) \Seq disk(Quantity)\\
    Capitalized &\Arrow string()\\
    Role &\Arrow string()\\
    Room &\Arrow integer()\\
    Quantity &\Arrow float()\\
  \end{aligned}
\end{equation*}
\newpage
